Supplementary Materials for Imminent range shifts in transboundary fish stocks challenge their management under climate change

### 2021-05-11 Scripts/Reviews/reviewer_three.Rmd
Initial round of revisions done

*Response:* William, thoughts?

>>>>

*Response:* Thank you for your comment. The transboundary index only captures the sharing stability over time. We had originally explored the directionality of the TI per stock, however, this was removed from the analysis as we rather focused on the "time of emergence" of the future TI from historical variability. Thus, since we do not talk about the directionallity of the TI (nor the TI *per se*) we have removed this sentence to avoid misunderstanding.

The equality of sharing is measured by the Stock Share Ratio described under *Quantifying the intensity of transboundary stocks’ range shift.*

### 2021-05-11 Scripts/Supplements.Rmd
Initial round of revisions done

Here, we adopt the concept of threat point to quantify the intensity of changes in the shared distribution of transboundary stocks between neighboring EEZs. The concept of threat point comes from Game Theory and has been widely used in shared fisheries management [@Bailey:2010ga; @Sumaila:2013hv; @Sumaila:2020tp; @Clark:1975uu; @Munro:1979dg]. In a game theoretic model, a player’s strategy (e.g., to act cooperatively or not) will have direct consequences for other players, which, in turn, will affect the overall outcome of the game [@Bailey:2010ga]. Cooperation will often result in the maximization of benefits for the system rather than for individual players. However, for a cooperative strategy to work, the benefit a player gets must not be less than the benefit under a non-cooperative strategy. Thus, the “threat point” is defined as the minimum payoff a player is willing to receive to cooperate in a game-theoretic model [@Nash:1953vr]. We define the threat point as the minimum required catch proportion of a transboundary stock within an EEZ for a country to engage in cooperative management with their sharing neighbor [@PalaciosAbrantes:2020vt; @Sumaila:2020tp]. Any proportion below the defined threat point would result in the unilateral management of the stock. First, we estimated the stock share ratio (SSR) of each transboundary stock shared by neighboring nations between 1951 and 2100. We did this by aggregating the projected catch within the $0.5^{\circ}$ x $0.5^{\circ}$ grid cells in which the stock is present across neighboring EEZs, and then calculated the proportion of the stock's catch held within each EEZ [@PalaciosAbrantes:2020tv]. Second, to reduce the effects of variability, we averaged the calculated proportion of stock occupying a given EEZ into three time periods: the historical time period ($SSR_{th}$) from 1951 to 2005, and two future periods, the early $21^{st}$ century, between 2021 and 2040 ($SSR_{te}$), and the mid $21^{st}$ century, defined as the average of 2041 to 2060 ($SSR_{tm}$). These future time periods were chosen to correspond to the challenges of achieving fisheries-relevant UN-SDGs by 2030 (i.e., the 2030 Agenda), such as SDG 14.4 (end overfishing), SDG 2.4 (ensure sustainable food production systems) and SDG 1.2 (poverty reduction) [@Singh:2017ds; @UnitedNations:1Qe8KIcN]. The analysis was replicated for projected stock distributions from each of the ten ensemble members and results were averaged across ensemble members. Third, we defined a threat point for each EEZ’s stock as $SSR_{th} \pm 2 \sigma$, where  is the standard deviation of $SSR_{th}$. Thus, a change of SSR beyond an EEZ’s threat point happens when the future SSR exceeds two standard deviations of the historical variations in SSR (i.e., when $SSR_{et} \geqq (SSR_{th} + 2 \sigma$) or $SSR_{e,m} \leqq (SSR_{th} - \sigma)$. Finally, we estimated the percentage change in SSR ($\Delta SSR$) of each future time period ($SSR_{tf}$) relative to the historic time period $SSR_{th}$ for each stock whose share ratio exceeded the threat point following [@PalaciosAbrantes:2020tv];

>>>>

Here, we adopt the concept of threat point to quantify the intensity of changes in the shared distribution of transboundary stocks between neighboring EEZs. The concept of threat point comes from Game Theory and has been widely used in shared fisheries management [@Bailey:2010ga; @Sumaila:2013hv; @Sumaila:2020tp; @Clark:1975uu; @Munro:1979dg]. In a game theoretic model, a player’s strategy (e.g., to act cooperatively or not) will have direct consequences for other players, which, in turn, will affect the overall outcome of the game [@Bailey:2010ga]. Cooperation will often result in the maximization of benefits for the system rather than for individual players. However, for a cooperative strategy to work, the benefit a player gets must not be less than the benefit under a non-cooperative strategy. Thus, the “threat point” is defined as the minimum payoff a player is willing to receive to cooperate in a game-theoretic model [@Nash:1953vr]. We define the threat point as the minimum required catch proportion of a transboundary stock within an EEZ for a country to engage in cooperative management with their sharing neighbor [@PalaciosAbrantes:2020vt; @Sumaila:2020tp]. **Any proportion below the defined threat point would result in the unilateral management of the stock assuming that no country will be willing to engage in cooperative management if the future catch proportion of the transboundary stock is lower than it has ever been.**

First, we estimated **the catch proportion as the** stock share ratio (SSR) of each transboundary stock shared by neighboring nations between 1951 and 2100. We did this by aggregating the projected catch within the $0.5^{\circ}$ x $0.5^{\circ}$ grid cells in which the stock is present across neighboring EEZs, and then calculated the proportion of the stock's catch held within each EEZ [@PalaciosAbrantes:2020tv]. Second, to reduce the effects of variability, we averaged the calculated proportion of stock occupying a given EEZ into three time periods: the historical time period ($SSR_{th}$) from 1951 to 2005, and two future periods, the early $21^{st}$ century, between 2021 and 2040 ($SSR_{te}$), and the mid $21^{st}$ century, defined as the average of 2041 to 2060 ($SSR_{tm}$). These future time periods were chosen to correspond to the challenges of achieving fisheries-relevant UN-SDGs by 2030 (i.e., the 2030 Agenda), such as SDG 14.4 (end overfishing), SDG 2.4 (ensure sustainable food production systems) and SDG 1.2 (poverty reduction) [@Singh:2017ds; @UnitedNations:1Qe8KIcN]. The analysis was replicated for projected stock distributions from each of the ten ensemble members and results were averaged across ensemble members. Third, we defined a threat point for each EEZ’s stock as $SSR_{th} \pm 2 \sigma$, where  is the standard deviation of $SSR_{th}$. Thus, a change of SSR beyond an EEZ’s threat point happens when the future SSR exceeds two standard deviations of the historical variations in SSR (i.e., when $SSR_{et} \geqq (SSR_{th} + 2 \sigma$) or $SSR_{e,m} \leqq (SSR_{th} - \sigma)$. Finally, we estimated the percentage change in SSR ($\Delta SSR$) of each future time period ($SSR_{tf}$) relative to the historic time period $SSR_{th}$ for each stock whose share ratio exceeded the threat point following [@PalaciosAbrantes:2020tv];
